---
title: "ShinyAppTutorial for Foundations of STS Engineering"
author: "Sarah Blum"
date: "January 27, 2018"
output: pdf_document
---

<!--
Sources:
- basic commands for R markdown:
http://rmarkdown.rstudio.com/authoring_rcodechunks.html,
- knitR cheat sheet:
https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf
- shiny cheat sheet:
http://shiny.rstudio.com/images/shiny-cheatsheet.pdf
- all cheat sheets from R in one place:
https://www.rstudio.com/resources/cheatsheets/

- examples of shiny Apps including tutorials and showcases
https://shiny.rstudio.com/gallery/
http://shiny.rstudio.com/tutorial/written-tutorial/lesson1/
-->

## Helpful Links for today
- shiny cheat sheet:
http://shiny.rstudio.com/images/shiny-cheatsheet.pdf

- all cheat sheets from R in one place:
https://www.rstudio.com/resources/cheatsheets/

- examples of shiny Apps including tutorials and showcases
https://shiny.rstudio.com/gallery/



## If you ever get stuck: Debugging Shiny Apps
To debug your Shiny App, you have several options available. The simplest is an unconditional breakpoint which interrupts the execution of your script:

```{r, eval=FALSE}
browser()
```

If your breakpoint has some conditions tied to it, then use:
```{r, eval=FALSE}
# Stop execution when the user selects "am"
browser(expr = identical(input$variable, "am"))
```
